%!TEX root = main.tex
\section{Introduction}

Most standard neural network models depart from the biological neuron in a number of ways. Our asynchronous continuous-time model draws inspiration from physiological and biological principles for neuron dynamics.

In a biological neuron, there are leak Na+ and K+ current channels that constantly push the neuron's voltage towards its equilibrium voltage. We have included an exponential decay term to model this homeostatic tendency towards equilibrium. Likewise, we have also loosely modelled the refractory period, the period immediately after an action period in which a neuron cannot send a signal, instead of having resetting the voltage of a neuron immediately back to zero.

There are many features of a biological neuron that we have chosen not to implement (most notably the dynamics of a neuron's voltage during a action potential, by implementing a Hodgkins-Huxley model (see wikipedia)) in that there is a trade-off between having a model that is more biological realisticity and one that is mathematically and computationally simple. There are projects like BlueBrain that aim for the most biologically realistic model, and a plethora of projects (deep learning, etc.) that are vaguely biologically inspired but have been massively implemented and successful at a small class of tasks. Our hope is by striving for a balance between the two ideals by implementing a system that is both biologically inspired and computationally simple, we would be able to make a massive implementation that succeeds in a wide variety of tasks that require both creativity and intelligence.

%\emph{Note:} 
%We need to motivate substantially the proposal of a drastically different framework of neurocomputation. This motivation should be given according to the latest neuroscience, and a general problem in the field.

%\todo[inline]{Argue against 
%the current state of ML's approach to the problem of AGI
%by surveying field.}
%\subsection{Intelligence as an Emergence Phenomenon}
%\todo[inline]{Establish Conwaynian philosophy on emergent neurocomputation.}
%\todo[inline]{Motivate asynchrynous neurocomputation.}
